Modelling Weddell Sea Food Web

### 2022-02-02 ModellingWeddellSea.Rmd
Updated function

#
# Read and check data available on GATEWAy about Weddell Sea
#
source("R/network_fun.r")
require(igraph)
require(dplyr)
require(multiweb)
require(readr)

# Read the original database
#
ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
names(ga)
wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name)) # %>% dplyr::select(con.taxonomy,con.taxonomy.level,res.taxonomy,res.taxonomy.level)
#saveRDS(wedd_df, "Data/wedd_df.rds")

@@

# Extract the birds from the network
#
require(taxize)
can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
aves <- class_names %>% filter( class =="Aves")

wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)
save.image()
```

@@

# Parameters for alometric equations @Emmerson2004 y ... 
# @Yang2019 --> Parametriza Lotka Volterra
# @Donohue2017 --> Parametriza model derived from Yodzis and Innes (1992), updated with more recent allometric coefficients
# @Fahimipour2014 ---> Estima el flujo a partir de la tasa metabólica y las densidad de la poblacion
# @Carrara2015  --> distintos metodos para estimar interacciones basados en LV
#
# @Petchey2008 LV Parametrization an interesting idea is that it adds Type 2 functional response to check structural robustness 
#
# @Brose2006 Parametrization of consumer–resource model (Yodzis & Innes 1992) updated with new allometric coefficients (Brown et al. 2004)
# and extended to multispecies systems (Williams & Martinez 2004b)
#
# @James2015 Uses @Emerson2004 as a method to get LV interaction strength using body masses 
#
# @Neutel2014 Uses LV parametrized from empirical data 
# @Pawar2012 ------------------------------------------------- YES

n0 <- -1.16 
g <- -0.75

# Make the body mass of Phytodetritus Sediment = 1e-14 to obtain better interaction rates for detritivores
#
wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))

res <- wedd_df %>% distinct(res.taxonomy, .keep_all = TRUE) %>% rename(name=res.taxonomy,mass_mean = res.mass.mean.g.) %>% select(name, mass_mean) 
con <- wedd_df %>% distinct(con.taxonomy, .keep_all = TRUE) %>% rename(name=con.taxonomy) %>% select(name, con.mass.mean.g.) 
con <- anti_join(con,res) %>% rename(mass_mean =con.mass.mean.g.)
wedd_sp <- bind_rows(res,con)

# Neq Multiplied by 1e8 to make min populations on the order of 1000, detritus set at big values
#
# Make the mass_mean of  Phytodetritus Sediment = 3e+07
#
wedd_sp <- wedd_sp %>% mutate(mass_mean=ifelse(mass_mean==1e-14,3e+07,mass_mean	 ),
  Neq = 10^(n0+g+rnorm(nrow(wedd_sp),0,0.2))*mass_mean^(g+1)*1e9) %>% arrange(desc(Neq)) %>% mutate(Num_eq=Neq/mass_mean)

require(ggplot2)
ggplot(wedd_sp, aes(Num_eq)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()

require(ggplot2)
ggplot(wedd_sp, aes(Neq)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()

# Generate interaction rates from wedd_df 
#
#
wedd_aij <- wedd_df %>% mutate(aij =  10^-3.5 * con.mass.mean.g. *( (res.mass.mean.g./con.mass.mean.g.)^0.46 / (1 + (res.mass.mean.g./con.mass.mean.g.)^2)) ) %>% select( res.taxonomy, con.taxonomy, aij) %>% arrange(desc(aij))

ggplot(wedd_aij, aes(aij)) +  geom_density(color="darkblue",fill="white") + theme_bw()

rm(res,con,can_names,class_names)
save.image()

wedd_aij %>% filter(con.taxonomy=="Fulmarus glacialoides") 
wedd_aij %>% filter(res.taxonomy=="Fulmarus glacialoides")

>>>>

#
# Read and check data available on GATEWAy about Weddell Sea
#
source("R/network_fun.r")
require(igraph)
require(multiweb)
require(tidyverse)

# Read the original database
#
ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
names(ga)
wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name))  #saveRDS(wedd_df, "Data/wedd_df.rds")

@@

# Extract the birds from the network
#
# require(taxize)
# can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
# class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
# aves <- class_names %>% filter( class =="Aves")
# 
# wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)

# Rename and Select fields

wedd_df <- wedd_df %>% rename(con_mass_mean=con.mass.mean.g.,res_mass_mean=res.mass.mean.g.,con_taxonomy=con.taxonomy,res_taxonomy=res.taxonomy,interaction_dim=interaction.dimensionality) %>% select(con_taxonomy,res_taxonomy, con_mass_mean,res_mass_mean,interaction_dim)

save.image()
```

@@

# Parameters for alometric equations @Emmerson2004 y ... 
# @Yang2019 --> Parametriza Lotka Volterra
# @Donohue2017 --> Parametriza model derived from Yodzis and Innes (1992), updated with more recent allometric coefficients
# @Fahimipour2014 ---> Estima el flujo a partir de la tasa metabólica y las densidad de la poblacion
# @Carrara2015  --> distintos metodos para estimar interacciones basados en LV
#
# @Petchey2008 LV Parametrization an interesting idea is that it adds Type 2 functional response to check structural robustness 
#
# @Brose2006 Parametrization of consumer–resource model (Yodzis & Innes 1992) updated with new allometric coefficients (Brown et al. 2004)
# and extended to multispecies systems (Williams & Martinez 2004b)
#
# @James2015 Uses @Emerson2004 as a method to get LV interaction strength using body masses 
#
# @Neutel2014 Uses LV parametrized from empirical data 
# @Pawar2012 2D/3D search space + metabolic theory

# Check detritus
#
detritus <- wedd_df %>% filter(grepl("tritus",res_taxonomy)) 
detritus <- wedd_df %>% filter(is.na(interaction_dim))
write_tsv(wedd_df %>% arrange(interaction_dim), "Data/Wedd_mass.dat")

wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )

#wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))

ggplot(wedd_int, aes(qRC)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()

ave.image()
